\documentclass{resume}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Andrew Robles}
\address{+1(805) 312-6420 \\ Los Angeles, CA} 
\address{\href{mailto:andrewrobles@berkeley.edu}{andrewrobles@berkeley.edu} \\ \href{https://linkedin.com/in/andrew-robles-dev}{linkedin.com/in/andrew-robles-dev} \\ \href{https://github.com/andrewrobles}{github.com/andrewrobles}}

\begin{document}
    \begin{rSection}{OBJECTIVE}
        {Software Engineer with 3+ years of experience in JavaScript and Python, open to full-stack or front-end web development roles.}
    \end{rSection}

    \begin{rSection}{Education}
        {\bf University of California, Berkeley}: Electrical Engineering and Computer Science, B.S. \hfill {May 2019}
    \end{rSection}

    \begin{rSection}{EXPERIENCE}
        \textbf{Full-Stack Developer} \hfill June 2022 - Present\\
        Apple\hfill \textit{Culver City, CA}
        \begin{itemize}
            \itemsep -3pt {} 
            \item Migrated front-end component library from Vue2 to Vue3 to allow half a dozen web apps to upgrade dependencies to latest version.
            \item Streamlined development workflow by decoupling API from cloud infrastructure by containerizing Kafka broker and MongoDB database.
            \item Created micro-service for consuming Kafka messages from software applications from various external departments. 
            \item Defined API endpoints to allow frontend to communicate with the MongoDB database.
        \end{itemize}
        \textbf{Full-Stack Developer} \hfill Dec 2021 - May 2022\\
        StringKing \hfill \textit{Gardena, CA}
        \begin{itemize}
            \itemsep -3pt {} 
            \item Minimized external API latency by decoupling functionality from views, parallelizing external server processes, and indexing database models.
            \item Increased test database nightly backup process speed by 4x by automating tedious container orchestration using an RSync celery task and the Kubernetes Python library.
            \item Eliminated redundant API client code by refactoring internal Python API client architecture to be able to handle both HTTP and domain-specific protocols.
        \end{itemize}
        \textbf{Full-Stack Developer} \hfill Sep 2019 - Dec 2021\\
        GBL Systems Corporation \hfill \textit{Camarillo, CA}
        \begin{itemize}
            \itemsep -3pt {} 
            \item Streamlined artificial intelligence R\&D by developing a service-oriented graphic user interface for a neural net.
            \item Modernized management of thousands of dollars worth of physical assets by developing a custom asset management web application
            \item Accelerated efficiency in the inventory department by drastically optimizing database search feature
            \item Automated over a dozen tedious operations by delivering web service APIs to electronic warfare engineers
        \end{itemize}
    \end{rSection} 

    \begin{rSection}{SKILLS}
        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
            Technologies & React, Vue, MongoDB, Express, Node, Django, Bootstrap, Swagger, Cypress, Puppeteer\\
            Languages & JavaScript, Python\\
        \end{tabular}
    \end{rSection}

    \begin{rSection}{PROJECTS}
        \vspace{-1.25em}
        \item \textbf{Gym Routine Builder} - {iOS app for building weight lifting routines built using React Native, Node, and MongoDB}
        \item \textbf{Food Ordering Website} - {Website for building/ordering a custom sandwich built using the Django Web Framework}
        \item \textbf{Online Test Taker} - {Website user interface for taking a short quiz and auto-grading built using React}
    \end{rSection} 
\end{document}
